\documentclass{bamboo}

\Document{
	\Title{Randomized Algorithms}
    \section{Random Variables and Expectation}
    Plucky has an $n$-sided die that will generate numbers in $\set{1, 2, \dots, n}$ uniformly at random. She is bored and she has decided to start and keep rolling her die until she has seen all the numbers in $\set{1,2, \dots, n}$  at least once. 
    
    We want to calculate how many die rolls it takes in expectation for Plucky to stop.
    
    For each $i\in\set{1, 2, \dots, n}$, we define a random variable $X_i$: its value is equal to the number of additional die rolls we need to see the $i$-th unique value after having already seen $i-1$ unique values.
        
    What is the type of probability distribution that the random variable $X_i$ follows? 
    \Choices {
    \Choice{Binomial}
    \Choice{Bernoulli}
    \Choice{Poisson}
    \Choice*{Geometric}
    }
    Assume Plucky has started rolling her die and she has seen $i - 1$ unique values so far. What is the probability of seeing a new number that she has not seen before in her next die roll? 
    \Choices{
    \Choice{$\frac{1}{n}$}
    \Choice{$\frac{i}{n}$}
    \Choice*{$\frac{n - i + 1}{n}$}
    \Choice{$\frac{1}{i - 1}$}
    }
    What is $\E{X_i}$? 
    \Choices{
    \Choice{$n$}
    \Choice{$\frac{n}{i}$}
    \Choice*{$\frac{n}{n - i + 1}$}
    \Choice{$i - 1$}
    }
    What is the expected total number of die rolls, until Plucky sees all the n values at least once? 
    \Choices{
    \Choice{$\Theta(n)$}
    \Choice*{$\Theta(n\log n)$}
    \Choice{$\Theta(n^2)$}
    \Choice{$\Omega(n^2\log n)$}
    }
    
    \section{Randomized Algorithms} 
    Can we use the random pivot selection idea in QuickSort for the selection problem?
    
    Assume we modify the $k$-select algorithm that we saw in previous lectures; instead of picking the pivot cleverly, we just pick a uniformly random element as the pivot each time. We call the resulting algorithm QuickSelect.
    
    What is the worst case runtime of QuickSelect? 
    \Choices{
    \Choice{$\Theta(n)$}
    \Choice{$\Theta(n\log n)$}
    \Choice*{$\Theta(n^2)$}
    \Choice{$\Omega(n^2\log n)$}
    }
    
    What is the probability that our random pivot partitions the array into two parts, each of size at most $\frac{3n}{4}$?
    \Choices {
        \Choice{$\frac{3}{4}\pm O(1/n)$}
        \Choice*{$\frac{1}{2}\pm O(1/n)$}
        \Choice{$\frac{1}{3}\pm O(1/n)$}
        \Choice{$\frac{1}{4}\pm O(1/n)$}
    }
    
    Assume we group QuickSelect's recursive calls into multiple phases. Phase $i$ is when the size of the array is in the interval
    \[ \left((3/4)^{(i + 1)}n, (3/4)^{i}n\right]. \]
    Note that we start at phase $0$ with an array of size $n$.
    
    For each phase we define a random variable $X_i$, whose value is the number of recursive calls in that phase. Using the answers to previous questions, calculate an upper bound for $\E{X_i}$. Which of the following is the (asymptotically) smallest upper bound on $\E{X_i}$?
    \Choices {
       	\Choice{$3+O(1/n)$}
    	\Choice*{$2+O(1/n)$}
    	\Choice{$n$}
    	\Choice{$O(\log n)$}
    }
    
    What is the expected (average case) runtime of QuickSelect? 
    \Choices{
    \Choice*{$\Theta(n)$}
    \Choice{$\Theta(n\log n)$}
    \Choice{$\Theta(n^2)$}
    \Choice{$\Omega(n^2\log n)$}
    }
}