\documentclass{bamboo}

\Document{
	\Title{Sorting Models}
    \section{3-Wise Comparisons} 
    Assume you have a function called 3-sort that takes as input an array of size $3$ of comparable objects and returns them in 
    sorted order. You want to sort an array of size $n \geq 3$ objects only using calls to 3-sort. How many function calls of 3-sort are
     required to sort an array of size n? Choose the asymptotically largest applicable lower bound.
    \Choices {
        \Choice{$\Omega(\log n)$}
        \Choice{$\Omega(\sqrt{n})$}
        \Choice{$\Omega(n)$}
        \Choice*{$\Omega(n\log n)$}
    }
    %-----
    \section{Possible or Impossible}
	Is it possible to implement the following algorithms or data structures? 


   A data structure that stores comparable objects and supports the following operations:
   \begin{itemize}
   	\item Insert new objects in $O(1)$ time per insertion.
   	\item Remove objects in $O(1)$ time per removal.
   	\item Return the smallest object currently in the collection in $O(1)$ time.
   \end{itemize}
   Is it possible to implement such a data structure?
   \Choices {
       \Choice{Possible}
       \Choice*{Impossible}
   }
   %-----
    An algorithm that runs in $O(n)$ time and takes an array $A$ of size $n$ of comparable objects, $i$, and $j$ ($1\leq i < j\leq n$) as inputs and returns all the elements that are greater than the $i$th smallest element in $A$ and less than the $j$th smallest element in $A$? 
    \Choices {
        \Choice*{Possible}
        \Choice{Impossible}
    }
    Which algorithm would be a good choice to use for the last part? 
    \Choices{
        \Choice*{$k$-Select}
        \Choice{Radix Sort}
        \Choice{Quick Sort}
        \Choice{Merge Sort}
    }
    %------
    An algorithm that runs in $O(n)$ time and takes an array $A$ of size $n$ of comparable objects and partitions $A$ into 
    $\frac{n}{\log n}$ groups of size  $\log n$ each, where for every $i<j$, members of group $i$ are smaller than or equal to members of group $j$.
    \Choices {
        \Choice{Possible}
        \Choice*{Impossible}
    }

    \section{Radix Sort and Counting Sort}

    Assume you have an array $A$ of size $n$ with positive integer element with all elements in the range $[1, n^3)$.
    
    What is the runtime of Counting Sort run on $A$? 
    \Choices {
        \Choice{$\Theta(n)$}
        \Choice{$\Theta(n\log n)$}
        \Choice{$\Theta(n^2)$}
        \Choice*{$\Theta(n^3)$}
    }
    What is the runtime of Radix Sort, using base $10$,  run on $A$? 
    \Choices {
        \Choice{$\Theta(n)$}
        \Choice*{$\Theta(n\log n)$}
        \Choice{$\Theta(n^2)$}
        \Choice{$\Theta(n^3)$}
    }
    Which base for Radix Sort will result in the fastest Radix Sort algorithm to sort $A$ with?
    \Choices {
        \Choice{$2$}
        \Choice{$10$}
        \Choice*{$n$}
        \Choice{$n^2$}
    }
}